---
title: "R Shiny Report"
output: html_document
---


```{r set-options, echo=FALSE, cache=FALSE}
```


### Attributes Summary

***
```{r ATTR_SUMMARY,fig.width= 16,fig.height= 6, echo= FALSE,warning=FALSE}

K = attr_ranked()
fit = cluster_fit()
labelx = labelx()
    D = rearrange(X = K, labelx, chisq_table())
Ncol = ncol(D)
Rows = floor(Ncol/5)

if("Attributes summary" %in% input$reportList){
    if(Rows>0){
      for(j in 1:Rows){
        local({
          my_i = j
          
          name = paste("row",my_i,sep="")

            y = y()
          
            for(i in 1:5){
              index=my_i*5-5+i
              assign(paste("p",i,sep=""),
                     barplot_1(D[,index],
                               y,
                               names(D)[index],
                               chisq_test(D[,index],y,nrow(D)*input$chisq_tol),
                               labelx,
                               NUM_CLUST_A(),
                               showbarcolor = input$showbarcolor
                     )#,envir = globalenv() 
              )
            }
            g = cbind(p1,p2,p3,p4,p5, size="first")
            g$heights = grid::unit.pmax(p1$heights, p2$heights,p3$heights,p4$heights,p5$heights)
            grid::grid.newpage()
            grid::grid.draw(g)
            
          
        })
      }
    }
    Nleft = Ncol%%5
    eachRow = 5
    N = NUM_CLUST_A()
    STATUS = y()
    
    if(Nleft>0){
    pvalues=c()
    pvalues[(Rows*eachRow+1):(Rows*eachRow+Nleft)] = sapply(1:Nleft, function(i){chisq_test(D[,Rows*eachRow+i],STATUS,floor(nrow(D)*input$chisq_tol))})
    }
    
    p0=ggplot(mtcars, aes(x = wt, y = mpg)) + geom_blank()+theme(
      panel.background = element_rect(fill = NA), 
      panel.grid = element_blank(),
      axis.title=element_blank(),
      axis.ticks=element_blank(),
      axis.text=element_blank()
    )
    p0 = ggplotGrob(p0)
    
    if(Nleft==1){
      pp1 = barplot_1( D[,Rows*eachRow+1],
                       STATUS,
                       names(D)[Rows*eachRow+1],
                       pvalues[Rows*eachRow+1],
                       labelx,
                       N,
                       showbarcolor = input$showbarcolor)
      gx = cbind(pp1, p0,p0,p0,p0, size="first")
      gx$heights = grid::unit.pmax(pp1$heights)
      
    }
    if(Nleft==2){
      pp1 = barplot_1( D[,Rows*eachRow+1],
                       STATUS,
                       names(D)[Rows*eachRow+1],
                       pvalues[Rows*eachRow+1],
                       labelx,
                       N,
                       showbarcolor = input$showbarcolor)
      
      pp2 = barplot_1( D[,Rows*eachRow+2],
                       STATUS,
                       names(D)[Rows*eachRow+2],
                       pvalues[Rows*eachRow+2],
                       labelx,
                       N,
                       showbarcolor = input$showbarcolor)
      
      gx = cbind(pp1, pp2,p0,p0,p0, size="first")
      gx$heights = grid::unit.pmax(pp1$heights,pp2$heights)
      
    }
    if(Nleft==3){
      pp1 = barplot_1( D[,Rows*eachRow+1],
                       STATUS,
                       names(D)[Rows*eachRow+1],
                       pvalues[Rows*eachRow+1],
                       labelx,
                       N,
                       showbarcolor = input$showbarcolor)
      
      pp2 = barplot_1( D[,Rows*eachRow+2],
                       STATUS,
                       names(D)[Rows*eachRow+2],
                       pvalues[Rows*eachRow+2],
                       labelx,
                       N,
                       showbarcolor = input$showbarcolor)
      
      pp3 = barplot_1( D[,Rows*eachRow+3],
                       STATUS,
                       names(D)[Rows*eachRow+3],
                       pvalues[Rows*eachRow+3],
                       labelx,
                       N,
                       showbarcolor = input$showbarcolor)  
      gx = cbind(pp1, pp2,pp3,p0,p0, size="first")
      gx$heights = grid::unit.pmax(pp1$heights,pp2$heights,pp3$heights)
      
    }
    if(Nleft==4){
      pp1 = barplot_1( D[,Rows*eachRow+1],
                       STATUS,
                       names(D)[Rows*eachRow+1],
                       pvalues[Rows*eachRow+1],
                       labelx,
                       N,
                       showbarcolor = input$showbarcolor)
      
      pp2 = barplot_1( D[,Rows*eachRow+2],
                       STATUS,
                       names(D)[Rows*eachRow+2],
                       pvalues[Rows*eachRow+2],
                       labelx,
                       N,
                       showbarcolor = input$showbarcolor)
      
      pp3 = barplot_1( D[,Rows*eachRow+3],
                       STATUS,
                       names(D)[Rows*eachRow+3],
                       pvalues[Rows*eachRow+3],
                       labelx,
                       N,
                       showbarcolor = input$showbarcolor)  
      pp4 = barplot_1( D[,Rows*eachRow+4],
                       STATUS,
                       names(D)[Rows*eachRow+4],
                       pvalues[Rows*eachRow+4],
                       labelx,
                       N,
                       showbarcolor = input$showbarcolor)  
      gx = cbind(pp1, pp2,pp3,pp4,p0, size="first")
      gx$heights = grid::unit.pmax(pp1$heights,pp2$heights,pp3$heights,pp4$height)
      
    }
      grid::grid.newpage()
      if(Nleft !=0) grid::grid.draw(gx)


}
```














***
### Attributes Clustering Chart
```{r ATTR_CLUST, echo=FALSE, fig.width= 16 , fig.height= 8,warning=FALSE}
if("Attributes clustering" %in% input$reportList) {
      p1 = ggdendrogram(as.dendrogram(fit), rotate=TRUE)
      df2<-data.frame(cluster=cutree(fit,NUM_CLUST_A()),states=factor(fit$labels,levels=fit$labels[fit$order]))
      df3<-ddply(df2,.(cluster),summarise,pos=mean(as.numeric(states)))
      p2 = ggplot(df2,aes(states,y=1,fill=factor(cluster)))+geom_tile()+
        scale_y_continuous(expand=c(0,0))+
        theme(axis.title=element_blank(),
              axis.ticks=element_blank(),
              axis.text=element_blank(),
              legend.position="none")+coord_flip()+
        geom_text(data=df3,aes(x=pos,label=cluster))
      gp1<-ggplotGrob(p1)
      gp2<-ggplotGrob(p2)  
      maxHeight = grid::unit.pmax(gp1$heights[2:5], gp2$heights[2:5])
      gp1$heights[2:5] <- as.list(maxHeight)
      gp2$heights[2:5] <- as.list(maxHeight)
      grid.arrange(gp2, gp1, ncol=2,widths=c(1/6,5/6))
}
```

***

### Two way barplot of selected attributes

```{r TWO_WAY, echo=FALSE, fig.width= 16 , fig.height= 8,warning=FALSE}
if( "Two way barplot" %in% input$reportList      &!is.null(input$factor_1)) {
        X = if(input$head_or_drive =="HEAD") ATTR() else ATTR_drive()
        y = y()      
        x1 = X[,input$factor_1]
        x2 = X[,input$factor_2]
        FAIL = y
        xname1 = input$factor_1
        xname2 = input$factor_2

      barplot_2(x1,x2,FAIL,xname1,xname2)
}
```

***


### Attributes with many levels

```{r MANY_LEVELS, echo=FALSE,warning=FALSE, fig.height=6,fig.width=12}
if( "Attributes with many levels" %in% input$reportList     &!is.null(input$factor_3)) {

    X = attr_many_levels()
    y = y()
  
    xname = input$factor_3
    
    x = as.character(X[,xname])
  
    p = barplot_1_custom(x,
                         y,
                         xname = xname,
                         chisq_test(x,y,nrow(X)*input$chisq_tol),
                         L=NULL,
                         
                         NUM_CLUST_A()
                         
    )
    
    grid::grid.newpage()
    grid::grid.draw(p)



      X = attr_many_levels()
      y = y()
      
      n = ncol(X)
      
      
      ListFails = function(x,y){
        D = data.frame(x,y)
        ddply(D,.(x), function(df) sum(df$y=="F"))$V1
      }
      
      LIST = lapply(X,function(x) ListFails(x,y))
      
      max_length = max(sapply(LIST, length))
      
      M_1 = lapply(LIST,function(x) c(x,rep("",max_length-length(x))))
      
      
      M_2 = t(data.frame(M_1))
      colnames(M_2) = paste0(1:ncol(M_2))
      library(DT)
      colfunc <- colorRampPalette(c("white", "red"))
      colors = colfunc(100)
      
      datatable(M_2,options =
                  list(
                    paging = FALSE,
                    ordering = FALSE,
                    filtering = FALSE,
                    searching =FALSE,
                    rownames = TRUE
                   )
                )%>% 
        formatStyle(
          paste0(1:ncol(M_2)),
          color = styleInterval(seq(0,3,length.out = 99), colors)
        )

}



```

***

###Parametrics Summary

```{r PARA_SUMMARY, echo=FALSE,warning=FALSE,out.width=c('300px', '300px','300px')}
#, fig.show='hold'}
#fig.width= 16,fig.height= 5,
if("Parametrics Summary" %in% input$reportList){
  D = scatterData()
  D = D[,sample(1:ncol(D))]
  FAIL = Y()
  highlight =   (FAIL == "F")
  
  color = scatter_color()
  
  n_pair = floor(ncol(D)/2)
  
  L = list()
  
  for ( i in 1:n_pair){
    x = D[,2*i-1]
    y = D[,2*i]
    namex = names(D)[2*i-1]
    namey = names(D)[2*i]
    temp = data.frame(x,y)
    temp2 = Random_Sample_prop(temp,0.1)
    temp3 = temp[highlight,]
    
    xcol = ggplotColours(NUM_CLUST_P())[  color[color[,1]==namex,2]      ]
    ycol = ggplotColours(NUM_CLUST_P())[  color[color[,1]==namey,2]      ]
    
    p = ggplot(data=temp2,aes(x=x,y=y)) +
      geom_point()+
      xlab(namex)+ ylab(namey)+
      geom_point(data=temp3,aes(x=x,y=y),color="red",size=4)+
      theme(legend.position="none")+
      theme(axis.title.x=element_text(colour=xcol))+
      theme(axis.title.y=element_text(colour=ycol))
    
    #assign(paste("p",i,sep=""),p)
    print(p)
    #L = c(L,list(p))
  }          
   # do.call(grid.arrange,c(L,ncol=3))
  
}
```

***

### Parametrics Clustering Chart

```{r PARA_CLUST, echo=FALSE, fig.width= 16 , fig.height= 6,warning=FALSE}
if("Parametrics clustering" %in% input$reportList){
      fit = para_clust_fit()
    p1 = ggdendrogram(as.dendrogram(fit), rotate=TRUE)
    
    df2<-data.frame(cluster=cutree(fit,h=0.5),
                    states=factor(fit$labels,levels=fit$labels[fit$order]))
    df3<-ddply(df2,.(cluster),summarise,pos=mean(as.numeric(states)))
    p2 = ggplot(df2,aes(states,y=1,fill=factor(cluster)))+geom_tile()+
      scale_y_continuous(expand=c(0,0))+
      theme(axis.title=element_blank(),
            axis.ticks=element_blank(),
            axis.text=element_blank(),
            legend.position="none")+coord_flip()+
      geom_text(data=df3,aes(x=pos,label=cluster))
    gp1<-ggplotGrob(p1)
    gp2<-ggplotGrob(p2)  
    maxHeight = grid::unit.pmax(gp1$heights[2:5], gp2$heights[2:5])
    gp1$heights[2:5] <- as.list(maxHeight)
    gp2$heights[2:5] <- as.list(maxHeight)
    grid.arrange(gp2, gp1, ncol=2,widths=c(1/6,5/6))
}


```

***

### Custom Scatterplot of selected Parametrics

```{r PARA_CUSTOM, echo=FALSE,fig.width= 16,fig.height= 8,warning=FALSE}
if("Custom Parametric Plot" %in% input$reportList){
    FAIL = Y()
    highlight =   (FAIL == "F")
    
    X = para()
    
    if(is.null(input$para_scatter_1) & is.null(input$para_scatter_2)){
      temp = data.frame(x = X[,1], y = X[,2])
      namex = names(X)[1]
      namey = names(X)[2]
    } else {
      temp = data.frame(x = X[,input$para_scatter_1], y = X[,input$para_scatter_2])
      namex = input$para_scatter_1
      namey = input$para_scatter_2
    }
    
    temp2 = Random_Sample_prop(  temp, 1)
    temp3 = subset(temp,highlight)
          
    ggplot(data=temp2,aes(x=x,y=y)) +
      geom_point(alpha=0.4)+
#       scale_x_continuous(limit=c(min(x), max(x)), 
#                          breaks=round(fivenum(x),1))+
#       scale_y_continuous(limit=c(min(y), max(y)),
#                          breaks=round(fivenum(y),1)) +    
      
      geom_rug(size=0.05) +   
      #geom_smooth(method=lm) +
      stat_ellipse(type = "norm",linetype = 2)+
      xlab(namex)+ ylab(namey)+
      theme_bw()+
      geom_point(data=temp3,aes(x=x,y=y),color="red",size=3)+
  geom_rug(data=temp3,size=0.1,color="red") +   
      theme(legend.position="none")
}
```


***

### Interactions Summary

```{r INTER_SUMMARY, echo=FALSE,fig.height=5,fig.width=12}
if("Interaction summary" %in% input$reportList & input$interaction){
  N = 50
  top_n = ifelse(  nrow(Interaction_DF())>N, N, nrow(Interaction_DF()))
  X = Interaction_DF()[1:top_n,]
  
  
  
  PARA_UNIQUE = unique(X$PARA)
  n = length(PARA_UNIQUE)
  Y = Y()

for(j in 1:n){
  
  my_i = j
  
  current_PARA = PARA_UNIQUE[my_i]
  temp = X[X$PARA == current_PARA, ]  
  m = nrow(temp)   
  
  #cat("<div'>")
  cat(current_PARA)
 # cat("</div>")
  
#  for(i in 1:m){
  P = lapply(1:m, function(i){
        attr_name = temp$ATTR[i]
        
        para_name = current_PARA
        
        attr = ATTR()[, attr_name ]
        
        para = para()[, para_name]
        
        PlotLogistGroup(attr,para,Y,
                        attr_name=attr_name,
                        para_name=para_name,
                        cutoff = 0.4,hide=1,uselog = input$inter_log) 
        #print(p)
        })

  do.call(grid.arrange,c(P,ncol=3))
  }
  
}
```

***

### Attribute-dominant custom plots
```{r out.width=c('450px', '450px'), fig.show='hold',echo=FALSE, warning=FALSE}
#```{r INTER_CUSTOM, echo=FALSE, fig.width= 16,fig.height= 8,warning=FALSE}
if("Attribute-Dominant Custom plots" %in% input$reportList       &!is.null(input$second_para)){
  
    attr = ATTR()[,input$dominant_attr]
    para = para()[,input$second_para]
    FAIL = Y()
    xname1 = input$dominant_attr
    xname2 = input$second_para

  p = PlotLogistGroup_jitter(attr,para,FAIL,xname1,xname2,0.4,1,uselog = input$dominant_ATTR_log)
  
    Group = ATTR()[,input$dominant_attr]
    y = para()[,input$second_para]
    
    xname1 = input$dominant_attr
    xname2 = input$second_para
            
    D = data.frame(Group,y)
    
    TT = paste("CDF  ",  xname2  ," by ", xname1 )
    p2 = ggplot(D, aes(x=y,colour = Group)) + stat_ecdf() +#+ theme(legend.position="none")
      theme(axis.title.x=element_blank(),axis.title.y=element_blank()) +
      scale_fill_discrete(name="Group")+
      ggtitle(TT)+
      theme(plot.title = element_text(size=15,color="blue"))
  print(p)
  print(p2)
  
}
```

***

### Attribute-dominant Rank
```{r out.width=c('450px', '450px'), fig.show='hold',echo=FALSE, warning=FALSE}
#```{r INTER_CUSTOM, echo=FALSE, fig.width= 16,fig.height= 8,warning=FALSE}
if("Attribute-Dominant Rank" %in% input$reportList){

  N = min(10,ncol(SECOND_PARAS()),na.rm = TRUE)

        # boxplot
        for(j in 1:N){
          my_i = j
          
          x = as.character(RAW()[,input$dominant_attr])
          y = SECOND_PARAS()[,my_i]
          
          
          D = data.frame(x,y)
          
          pvalue = tryCatch({
            fit = aov(y ~ x)
            summary(fit)[[1]][[1,"Pr(>F)"]]
          }, error = function(e){
            1
          })
          
          TT = paste(names(SECOND_PARAS())[my_i],"    ANOVA p-value:",round(pvalue,3),sep=" ")
          
          p = ggplot(D, aes(factor(x), y))+geom_boxplot()+geom_jitter()+
              xlab(input$box_attr) + ggtitle(TT)+
              theme(plot.title = element_text(size=15,color="blue"),
                    axis.title.y=element_blank(),
                    axis.text.x = element_text(angle = 90, hjust = 0)
              )
                      if (input$dominant_ATTR_log){
                        #p = p + scale_y_continuous(trans = log_trans())
                        p = p + scale_y_log10()
                      }
          
        #cdf
        
          Group = as.character(RAW()[,input$dominant_attr])
          y = SECOND_PARAS()[,my_i]
          
          D = data.frame(Group,y)
          
          TT = paste("CDF  ",  names(SECOND_PARAS())[my_i]  ," by ",input$dominant_attr )
                    
          p2 = ggplot(D, aes(x=y,colour = Group)) + stat_ecdf() +#+ theme(legend.position="none")
              theme(axis.title.x=element_blank(),axis.title.y=element_blank()) +
              scale_fill_discrete(name="Group")+
              ggtitle(TT)+
              theme(plot.title = element_text(size=15,color="blue"))
        
        print(p)
        print(p2)
      }
  
  
}
```


***


### Parametric-dominant custom plots

```{r out.width=c('450px', '450px'), fig.show='hold',echo=FALSE, warning=FALSE}
#```{r INTER_ALL, echo=FALSE, fig.width= 16,fig.height= 8}
if("Parametric-Dominant Custom plots" %in% input$reportList          &!is.null(input$second_attr)){

    attr = ATTR()[,input$second_attr]
    para = para()[,input$dominant_para]
    FAIL = Y()
    xname1 = input$second_attr
    xname2 = input$dominant_para
    
    p = PlotLogistGroup_jitter(attr,para,FAIL,xname1,xname2,0.4,1,uselog = input$dominant_PARA_log)

    
    Group = ATTR()[,input$second_attr]
    y = para()[,input$dominant_para]
    
    xname1 = input$second_attr
    xname2 = input$dominant_para
    
    D = data.frame(Group,y)
    
    TT = paste("CDF  ",  xname2  ," by ", xname1 )
    p2 = 
      ggplot(D, aes(x=y,colour = Group)) + stat_ecdf() +#+ theme(legend.position="none")
      theme(axis.title.x=element_blank(),axis.title.y=element_blank()) +
      scale_fill_discrete(name="Group")+
      ggtitle(TT)+
      theme(plot.title = element_text(size=15,color="blue"))
    print(p)
    print(p2)
}

```

***


### Parametric-dominant rank

```{r out.width=c('450px', '450px'), fig.show='hold',echo=FALSE, warning=FALSE}
#```{r INTER_ALL, echo=FALSE, fig.width= 16,fig.height= 8}
if("Parametric-Dominant Rank" %in% input$reportList){

    N = min(10,ncol(SECOND_ATTRS()),na.rm = TRUE)
    
        for(j in 1:N){
          my_i = j
          

          #boxplot
          x = SECOND_ATTRS()[,my_i]
          y = RAW()[,input$dominant_para]
          
          
          D = data.frame(x,y)
          

          pvalue = tryCatch({
            fit = aov(y ~ x)
            summary(fit)[[1]][[1,"Pr(>F)"]]
          }, error = function(e){
            1
          })
          
          TT = paste(names(SECOND_ATTRS())[my_i],"    ANOVA p-value:",round(pvalue,3),sep=" ")
          
            p = ggplot(D, aes(factor(x), y))+geom_boxplot()+geom_jitter()+
              xlab(input$box_attr) + ggtitle(TT)+
              theme(plot.title = element_text(size=15,color="blue"),
                    axis.title.y=element_blank(),
                    axis.text.x = element_text(angle = 90, hjust = 0)
              )
                      if (input$dominant_PARA_log){
                        #p = p + scale_y_continuous(trans = log_trans())
                        p = p + scale_y_log10()
                      }
          #cdf
          
          Group = SECOND_ATTRS()[,my_i]
          y = RAW()[,input$dominant_para]
          
          D = data.frame(Group,y)
          
          
          TT = paste("CDF  ",  names(SECOND_ATTRS())[my_i]  ," by ",input$dominant_para )
          
          p2 = ggplot(D, aes(x=y,colour = Group)) + stat_ecdf() +#+ theme(legend.position="none")
              theme(axis.title.x=element_blank(),axis.title.y=element_blank()) +
              scale_fill_discrete(name="Group")+
              ggtitle(TT)+
              theme(plot.title = element_text(size=15,color="blue"))

          print(p)
          print(p2)
      }
}

```


Contact:ning.h.he@seagate.com